% !TEX root = ../thesis.tex
% \chapter{Results and discussion}
\chapter{Surface-surface interaction based separation of magnetic particles}
\section{Characterization of superparamagnetic particles}
\subsection{Zeta potential}
\subsection{Magnetophoretic velocity}
\section{Transport dynamics close to the surface}
\subsection{Mean ensemble velocity}\label{subsection:mean_velocity}

In this Section, the mean velocity $\left< v \right>$ of the particle ensemble transported close to the substrate's surface will be the main focus. 
It will be presented how the mean velocity is calculated considering a constant video duration, but with a varying number of steps each particle can take, or with a constant number of steps but, therefore, a varying video duration.
It will be shown that keeping the number of steps constant has benefits while granting a reasonably high statistic.



\section{Transport of magnetic particles bound to proteins}
A major step towards a useful \ac{LOC} system is to prove that \acp{MP} can, indeed, be distinguished in their transport properties once bound to molecules. 
The following chapter will answer the question of how to efficiently transport proteins bound to particles and, consequently, how to detect that binding.
A mean velocity analysis similar to the one shown in Section \ref{subsection:mean_velocity} will be presented further, cementing the feasibility of the transport and detection concept.
The influence of different protein concentrations will be discussed, comparing Zeta potentials and the mean ensemble transport velocities.


\subsection{Sample preparation}

\subsection{Physiological conditions for proteins}


\subsection{Influence on Zeta potential?}
\subsection{Transport dynamics?}

\chapter{Particle transport on tissue}
\section{Sample preparation}
\section{Transport dynamics}

\subsection{Steady-state velocity?}

\chapter{White light interferometer for absolute height determination?}




